State of the Practice for Lattice Boltzmann Method Software

### 2022-02-07 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Additional edits to Section 5 on comparing LBM to research software for artifacts

Seventeen of the software packages explicitly reference domain theory, but a
full requirements specification, in the software engineering sense
\citep{IEEE1998, RobertsonAndRobertson1999Vol, ESA1991}, is absent from all of
the projects. Software packages that include a subset of a requirements
specification, such as DL\_MESO (LBE), keep the information brief and include it
within other documents. When present, theory related information is generally
found within a user manual, on a web-page, or in a cited publication. In the
latter case significant time may be needed to track down the information.

@@

Tutorials are available for 19 of the software packages. Generally they are
linearly written and easy to follow. However, only eight tutorials provide an
expected output. It is not possible to verify the correctness of the output of
the software packages that are missing this key information. In these cases the
user may need to assume correctness if there are no visible errors.

@@

\section{Comparison of Artifacts to Research Software in General}
\label{Sec_CompareArtifacts}

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, less common, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Less common artifacts were found in 8 to 15 (30-63\%)
of the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages. In this section we answers \rqref{RQ_CompareArtifacts} by
comparing the artifacts that we observed in LBM repositories to those observed
and recommended for research software in general.

\begin{table}
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Dependency Notes & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual / Guide & Requirements Spec.\\
Makefile / Build File & Version Control & \\
README File & & \\
License & & \\
Tutorial & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

The top four ranked packages do not have many of the rare artifacts. None of the
top four packages have any explicit API documentation. Three of these packages
(ESPREsSo, Ludwig, Palabos) have information on contributing to the project. Two
of them (OpenLB, Palabos) have a FAQ section or forum. One (OpenLB) has
verification and validation notes, and a video guide of the software.

\wss{Change to clarify that it is theory notes, not a requirements
specification.  Remove requirements spec from table and put it as rare.}

\wss{** Requirements **}
\wss{Discuss requirements here. Extra information from Peter: I interpreted it
to mean what the software should do. As noted in my report, this was not common,
especially finding any formal document like an SRS. I do not recall any package
having an SRS. Some packages did note in their manuals or artifacts some of the
points that would be found in an SRS document. For example, DL\_MESO notes
functional (``The following is a list of the features that DLMESO currently
supports....'') and non-functional (should work in both ``serial and parallel
running; it can be run on standalone machines, clusters and supercomputers..'')
requirements in its documentation (more on this below). Yes, there was often
some sort of a theory resource. Often it was simply a link or reference to the
theory used in the package. There was significant discrepancy in how much theory
was documented or referenced. Meanwhile, requirements were rare. A few packages
did note some of this information within other artifacts but it was not
comprehensive, and it was not presented in a SRS document. DL\_MESO has some of
the information that belongs in an SRS in its user manual. It is not
comprehensive or presented as it would be in an SRS, but it was probably the
best example of requirements. It has a nice subsection on Functionality.
\citet{Nguyen-HoanEtAl2010} showed requirements are the least commonly produced
type of documentation for scientific software in general.  LBM matches this
trend.}

\wss{Document theory (17 of the packages), but not requirements.  Might think
 this is good enough, but a theory manual doesn't include the traceability to
 the code.  For instance, what are the consequences of changing an assumption?}

 \wss{Kelly paper about how researchers document their theory.  Close to being enough - just need traceability and other things.}

@@

\wss{README files discussed in PranaEtAl2018.}

\wss{At some point should get into the intended use of the software.  The
artifacts will change depending on the intention for the software.  Maybe just
say at the start that writing as if all software is intended for research
readiness?}

\wss{From Peter: Roadmap - I did see this mentioned, but no specific artifacts
for it. (``rare'' mentions) Code of conduct, policies for team members - do not
recall ever seeing this Citation - definitely saw this several times (``less
common'') Programming style guide - I did see this as part of developers guide
(``rare'') description of team processes - I do recall seeing ``workflow'' detailed
(``rare''). Not sure if this is similar. peer review - This was mentioned a few
times in the interviews, but I do not recall seeing artifacts for this.
checklists - I did see this a few times (``rare'') linters - I did see this
(``rare'') uninstall - I do not recall seeing this.}

@@

Answers \rqref{RQ_CompareToolsProjMngmnt}.  Software tools are used to support
the development, verification, maintenance, and evolution of software, software
processes, and artifacts \citep{ghezzi1991fundamentals}. Many tools are used by
LBM software packages, as summarized in Table~\ref{tbl_tools}.  The tools are
subdivided into development tools, dependencies, and project management tools.

@@

Section \ref{SecSurfCorrectAndVerifiab} shows that continuous integration is
rare in LBM.

@@

The developers that were interviewed all noted similar project management
processes. In teams of only a couple of developers, additions of new features or
major changes are discussed with the entire team. Projects with more than a
couple developers have lead developer roles. These lead developers review
potential additions to the software. One of the developers (ESPResSo) that was
interviewed noted that an ad hoc peer review process is used to assess major
changes and additions.

@@

practices by the best measured.

\begin{itemize}
	\item The top projects provide great examples of achieving installability,
	by taking such steps as: providing complete installation instructions,
	writing instructions as if the user does not have any of the dependencies
	installed, automation of the installation process (for instance using make),
	including descriptive error message, and including steps for uninstallation.
	\item Surface Correctness and Verifiability. Make public (on package website
	or GitHub) the requirements specification document, or explicitly reference
	the domain theory that the software is designed from.  This was done by
	several top ranked packages, including ESPResSo, Ludwig, LUMA, and OpenLB.
	\item Surface Correctness and Verifiability. Ensure the above information is
	easy to find. Consider adding it to the user manual. The information is easy
	to find in most top ranked packages.
	\item Surface Correctness and Verifiability. Development teams should
	include both domain experts and experienced software developers. This
	suggestion is based on developer comments.
	\item Surface Correctness and Verifiability. Traceability. Visibility and
	Transparency. Use and make public (on package website or GitHub) detailed
	documentation. Consider using automatic document generation tools like
	Doxygen, Drasil, or Sphinx. This was done by all of the top five ranked
	packages.
	\item Surface Correctness and Verifiability. Provide detailed tutorials that
	include expected output, like the
	\href{https://www.walberla.net/doxygen/index.html}{waLBerla tutorials}.
	\item Surface Correctness and Verifiability. Use unit tests during
	development and make them public (on package website or GitHub). This was
	available for Ludwig.
	\item Surface Correctness and Verifiability. Modularize the source code,
	separate components, hide information behind well defined interfaces. This
	is suggested in SCS literature, and in developer comments.  \wss{one of
	Wilson's best practices.}
	\item Surface Understandability. Maintainability.  Modifiability.
	Reusability. Modularize the source code, separate components, hide
	information behind well defined interfaces. This is suggested in SCS
	literature, and in developer comments. \wss{add citation - Wilson mentions -
	this points seems repetitive}
	\item Surface Correctness and Verifiability. Use continuous integration
	tools (Bamboo, Jenkins, and Travis CI) and processes during development.
	This was done by top ranked packages ESPResSo and Ludwig.  \wss{Common in
	LBM - more common than in other domains}
	\item Surface Usability. State appropriate fluid dynamics problems that the
	software is designed to model in the documentation, and explicitly state the
	limits of the software. This is done in the ESPResSo user guide.
	\item Surface Usability. Provide documentation that details the background
	theory information, or provide a reference to such information. This was
	done by several top ranked packages, including ESPResSo, Ludwig, LUMA, and
	OpenLB.
	\item Surface Usability. Identify expected user characteristics. LIMBES,
	Ludwig, laboetie, and Palabos did this. The importance of specifying user
	characteristics is discussed in \citep{smith2007requirements}.
	\item Surface Usability. Keep all documentation in one location. This was
	done by top ranked packages.
	\item Surface Usability. Maintain a user support model (Git, email, forum,
	FAQ). This was done by all of the top five ranked packages.
	\item Surface Usability. If possible, consider using popular user-friendly
	software languages like Python. Especially consider this for parts of the
	source code that is likely to be modified or reviewed by users. ESPResSo and
	Sailfish use Python to shorten development time and improve usability.
	\item Maintainability. Include version numbers and release notes for all
	major source code and artifact releases. The top five ranked software
	packages include release notes.
	\item Maintainability. Have a defined process for accepting contributions,
	and make public documentation for making contributions to the project. The
	top five ranked software packages include information on how to contribute. 
	\item Maintainability. Use an issue tracker (Git, email, SourceForge, other)
	to manage bugs and changes. Issues should be regularly reviewed and closed.
	All but three (laboetie, lettuce, Sailfish) of the software packages that
	use Git have most of their issues closed.
	\item Maintainability. Use a version control system (GitHub, CVS). Four
	(ESPREsSo, Ludwig, LUMA, Palabos) of the top five ranked packages use a
	version control system.
	\item Maintainability. Source code needs to be well commented. Typically,
	more than 10 percent of LBM package source code is comments, as presented in
	Table~\ref{gitrepodata}. Four of the top five overall ranked packages
	(Ludwig, ESPResSo, Palabos, OpenLB) have about 20 percent of their source
	code as comments.
	\item Maintainability. If possible, consider using popular user-friendly
	software languages like Python. Especially consider this for parts of the
	source code that is likely to be modified or reviewed by users. ESPResSo and
	Sailfish use Python to address several software qualities, including
	maintainability.
	\item Modifiability. Consider flexibility of data structures and data
	storage in the design stage. The package pyLBM redeveloped data structures
	to ease future changes.
	\item Reusability. Provide API documentation, if applicable. Only one
	(ESPResSo) of the top five ranked packages provided API documentation.
	\item Surface Understandability. Adopt a coding standard and document it in
	artifacts, including some examples. A coding standard needs to be part of
	continuous integration. Only LUMA, HemeLB, and Musubi explicitly identify
	coding standards. 
	\item Surface Understandability. Add meaningful comments. Indicate what is
	being done in each section of source code. All of the top ranked packages
	have meaningful comments in their source code.
	\item Surface Understandability. State appropriate fluid dynamics problems
	that the software is designed to model in the documentation, and explicitly
	state the limits of the software. This is done in the ESPResSo user guide. 
	\item Surface Understandability. Consider adding a FAQ section to the
	documentation. This helped resolve some usability issues for OpenLB.
	\item Traceability. Provide a developer's guide to help orient developers to
	the artifacts, source code, and system architecture so that they can better
	document changes. Top ranked package OpenLB has a developer guide. \wss{How
	is this related to traceability?}
	\item Visibility and Transparency. Summarize the development process that is
	used. Provide information on how new users can contribute. Identify the
	development model by name (waterfall, agile, etc.), if appropriate.  Seven
	of the software packages have some artifacts outlining the general
	development process. Eleven packages have information on how to contribute. 
	\item Visibility and Transparency. Identify the development environment.
	Eight of the 24 software packages identify the development environment.
	\item Visibility and Transparency. Include notes with all releases. Nine of
	the packages include release notes.
	\item Visibility and Transparency. Communicate all changes within the
	development team. This suggestion is based on developer comments.
	\item Visibility and Transparency. Use continuous integration processes and
	tools (Bamboo, Jenkins, and Travis CI). This was done by top ranked packages
	ESPResSo and Ludwig.
	\item Visibility and Transparency. Consider peer review processes to assess
	contributions and ensure the tracking of information. High ranked package
	ESPResSo uses a peer review process for contributions. 
	\item Reproducibility. Test output against automatically calculated or known
	correct results. High ranked package ESPResSo does this.
	\item Reproducibility. Automate the testing of output. Run tests after all
	code changes. High ranked package ESPResSo does this.
	\item Reproducibility. Consider peer review processes and task based
	inspection to assess contributions. High ranked package ESPResSo does this.
	\item Unambiguity. State appropriate fluid dynamics problems that the
	software is designed to model in the documentation, and explicitly state the
	limits of the software. This is done in the ESPResSo user guide.
	\item Unambiguity. The documentation should either explain the underlying
	CFD theories or provide a reference to appropriate resources. This was done
	by several top ranked packages, including ESPResSo, Ludwig, LUMA, and
	OpenLB.
	\item Unambiguity. Consider asking users for feedback on the documentation.
	The developer of pyLBM noted that such feedback would be appreciated.

@@

@@

@@

>>>>

Seventeen of the software packages explicitly reference domain theory, but a
full and rigorous requirements specification, in the software engineering sense
\citep{IEEE1998, RobertsonAndRobertson1999Vol, ESA1991}, is absent from all of
the projects. Software packages that include a subset of a requirements
specification, such as DL\_MESO (LBE), keep the information brief and include it
within other documents. When present, theory related information is generally
found within a user manual, on a web-page, or in a cited publication. In the
latter case significant time may be needed to track down the information.

@@

Tutorials are available for 19 of the software packages. Generally they are
linearly written and easy to follow. However, only eight tutorials provide an
expected output. It is not possible to verify the correctness of the output of
the software packages that are missing this key information. In these cases the
user may need to assume correctness if there are no visible errors.  A
particularly  detailed tutorial that include expected output is provided by
\href{https://www.walberla.net/doxygen/index.html}{waLBerla}.

@@

\section{Comparison Between LBM and Research Software for Artifacts}
\label{Sec_CompareArtifacts}

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, less common, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Less common artifacts were found in 8 to 15 (30-63\%)
of the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages.  In this section we answers \rqref{RQ_CompareArtifacts} by
comparing the artifacts that we observed in LBM repositories to those observed
and recommended for research software in general. Our comparison may point out
areas where some LBM software packages fall short of current best practices.
This is not intended to be a criticism of any existing packages, especially
since in practice not every project needs to achieve the highest possible
quality.  However, rather than delve into the nuances of which software can
justify compromising which practices we will write our comparison under the
ideal assumption that every project has sufficient resources to match best
practices.

\begin{table}
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Library Dependency List & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual / Guide & Requirements Spec.\\
Makefile / Build File & Version Control & \\
README File & & \\
License & & \\
Tutorial & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

The top four ranked packages do not have many of the rare artifacts. None of the
top four packages have any explicit API documentation. Three of these packages
(ESPREsSo, Ludwig, Palabos) have information on contributing to the project. Two
of them (OpenLB, Palabos) have a FAQ section or forum. One (OpenLB) has
verification and validation notes, and a video guide for the software.

The majority of LBM generated artifacts correspond to general recommendations
from research software developers.  A union of the three columns in
Table~\ref{artifactspresent} mostly corresponds to recommendations made by the
research software community.  Most of the items in Table~\ref{artifactspresent}
are included in guidelines for writing research software, such as the DLR
(German Aerospace Centre) Software Engineering Guidelines
\citep{TobiasEtAl2018}, xSDK (Extreme-scale Scientific Software Development Kit)
Community Package Policies \citep{SmithAndRoscoe2018}, the EURISE (European
Research Infrastructure Software Engineers') Network Technical Reference
\cite{ThielEtAl2020} and CLARIAH (Common Lab Research Infrastructure for the
Arts and Humanities) Guidelines for Software Quality \citep{vanGompelEtAl2016}.
As an example, LBM developers list the external libraries on which the software
depends as recommended by \citet{BrettEtAl2021}, \citet{SmithAndRoscoe2018} and
\citet{vanGompelEtAl2016}. Although in the rare column, some LBM developers
include an FAQ (Frequently Asked Questions) document as recommended by
\citep{OrvizEtAl2017}, \citep{ThielEtAl2020} and \citep{vanGompelEtAl2016}. LBM
developers also follow the ubiquitous recommendation to have a README file,
although, as for other software, the content of README files is not standardized
\citep{PranaEtAl2018}.

Three of the items that appear in Table~\ref{artifactspresent} do not explicitly
appear in the software development guidelines: i) list of related publications,
ii) performance information and iii) video guides.  The occurrence of the first
two items in this list are likely more a consequence of how we collected our
list of LBM artifacts, rather than being a unique practice of LBM developers. We
highlighted publications and performance information because we were explicitly
looking for both as part of filling in our measurement template. Related
publications and performance information certainly appear in other research
software projects; the practices just aren't highlighted in guidelines because
they are implicit in other documentation recommendations, such as theory
documentation and user guides. The observation of a video guide artifact is more
novel.  Other projects likely use videos, but the practice has apparently not
yet made it into community guidelines.  Putting aside the debate of the
effectiveness of learning from print versus video, video documentation is
growing in popularity, with a majority of Generation Z learners preferring video
to print \citep{Genota2018}.

Although the LBM community participates in most of the practices we found listed
in general research software guidelines, some recommended practices were not observed or rarely observed. In addition to the items in the last column of Table~\ref{artifactspresent}, we can add the following community recommended items that we rarely, if ever, observed:

\begin{itemize}
\item A roadmap showing what is planned for the future \citep{Yo2021,
ThielEtAl2020, vanGompelEtAl2016}.  We did see this information mentioned in
some repos, but we did not observe a specific artifact devoted to this purpose.
\item A code of conduct to explicitly say how developers should treat one
another \citep{Yo2021, ThielEtAl2020}.  We did not observe a policy of this
sort, possibly because the number of developers for each LBM project is small.
\item Programming style guidelines so that programming labels and formatting are
consistent \citep{TobiasEtAl2018, ThielEtAl2020, OrvizEtAl2017, Zadka2018,
vanGompelEtAl2016, WilsonEtAl2014}.  We saw this information as part of
developer guides, but only rarely.
\item Checklists can be used in projects to ensure that best practices are
followed by all developers.  Some examples include checklists merging branches
into master \citep{Brown2015}, checklists for saving and sharing changes to the
project \citep{WilsonEtAl2016}, checklists for new and departing team members
\citep{HerouxAndBernholdt2018}, checklists for processes related to commits and
releases \citep{HerouxEtAl2008} and checklists for overall software quality
\citep{ThielEtAl2020, SSI2022}.  We did see evidence of checklists in the LBM
projects, but they were used only rarely.
\item Although not observed for LBM projects, having instructions to uninstall
the software is part of best practices \citep{vanGompelEtAl2016}.
\end{itemize}

The above discussion shows that, taken together, LBM projects fall short of
recommended practices for research software.  However, LBM software is not alone
in this.  Info on req, design and testing.  \citet{Nguyen-HoanEtAl2010} showed
requirements are the least commonly produced type of documentation for
scientific software in general.  Carver points out do not do requirements.  Not
everyone recommends requirements - can find citations.  Feasible to do
requirements.  Theory documents are already common (17 of 24? packages).  Need
to add just a little more information.

\wss{Document theory (17 of the packages), but not requirements.  Opportunity to
 go a little further and have a more complete requirements specificaiton. Add
 traceability to the code.  For instance, what are the consequences of changing
 an assumption?  adding an abstract transformation from theorty to code - when
 and how.  Example have a PDE, sate use finite difference. Consequence of change
 - likely and unlikely changes - give example of 2D vs 3D.  Basic idea is to
 give information on some simple things to add that would make a theory document
 like a requirements document. }

@@

In Table~\ref{artifactspresent} a rigorous requirements specification is rare,
but parts of a full specification do occur, with theory notes being common and
portions of the functional specification (statements about what the software
does) being less common.  Discuss requirements stuff.

@@

Software tools are used to support the development, verification, maintenance,
and evolution of software, software processes, and artifacts
\citep{ghezzi1991fundamentals}. Many tools are used by LBM software packages, as
summarized in Table~\ref{tbl_tools}.  The tools are subdivided into development
tools, dependencies, and project management tools.  In this section we answers
\rqref{RQ_CompareToolsProjMngmnt} by comparing the tool usage in LBM software to
the utilization in the research software community in general.

@@

Section \ref{SecSurfCorrectAndVerifiab} shows that continuous integration is
rare in LBM.  Recommended by many \citep{vanGompelEtAl2016} etc.

@@

The developers that were interviewed all noted similar project management
processes. In teams of only a couple of developers, additions of new features or
major changes are discussed with the entire team. Projects with more than a
couple developers have lead developer roles. These lead developers review
potential additions to the software. One of the developers (ESPResSo) that was
interviewed noted that an ad hoc peer review process is used to assess major
changes and additions.  Peer review (also known as code review and technical
review) is a frequently recommended component of developing research software
\citep{HerouxEtAl2008, Givler2020, OrvizEtAl2017, USGS2019}.

@@

practices by the best measured.  Point to existing checklist and development
guides.  This section should only mention things that are new.

\begin{itemize}
	\item Surface Correctness and Verifiability. Development teams should
	include both domain experts and experienced software developers. This
	suggestion is based on developer comments.
	\item Surface Correctness and Verifiability. Surface Understandability.
	Maintainability.  Modifiability. Reusability.  Modularize the source code,
	separate components, hide information behind well defined interfaces. This
	is suggested in SCS literature, and in developer comments.  \wss{one of
	Wilson's best practices.}
	\item Surface Usability. Surface Understandability. Unambiguity. State
	appropriate fluid dynamics problems that the software is designed to model
	in the documentation, and explicitly state the limits of the software. This
	is done in the ESPResSo user guide.
	\item Surface Usability. Provide documentation that details the background
	theory information, or provide a reference to such information. This was
	done by several top ranked packages, including ESPResSo, Ludwig, LUMA, and
	OpenLB.
	\item Surface Usability. Identify expected user characteristics. LIMBES,
	Ludwig, laboetie, and Palabos did this. The importance of specifying user
	characteristics is discussed in \citep{smith2007requirements}.
	\item Surface Usability. Keep all documentation in one location. This was
	done by top ranked packages.
	\item Maintainability. Have a defined process for accepting contributions,
	and make public documentation for making contributions to the project. The
	top five ranked software packages include information on how to contribute. 
	\item Modifiability. Consider flexibility of data structures and data
	storage in the design stage. The package pyLBM redeveloped data structures
	to ease future changes.
	\item Reusability. Provide API documentation, if applicable. Only one
	(ESPResSo) of the top five ranked packages provided API documentation.
	\item Surface Understandability. Adopt a coding standard and document it in
	artifacts, including some examples. A coding standard needs to be part of
	continuous integration. Only LUMA, HemeLB, and Musubi explicitly identify
	coding standards. 
	\item Traceability. Provide a developer's guide to help orient developers to
	the artifacts, source code, and system architecture so that they can better
	document changes. Top ranked package OpenLB has a developer guide. \wss{How
	is this related to traceability?}
	\item Visibility and Transparency. Summarize the development process that is
	used. Provide information on how new users can contribute. Identify the
	development model by name (waterfall, agile, etc.), if appropriate.  Seven
	of the software packages have some artifacts outlining the general
	development process. Eleven packages have information on how to contribute. 
	\item Visibility and Transparency. Consider peer review processes to assess
	contributions and ensure the tracking of information. High ranked package
	ESPResSo uses a peer review process for contributions. 
	\item Reproducibility. Test output against automatically calculated or known
	correct results. High ranked package ESPResSo does this.
	\item Reproducibility. Automate the testing of output. Run tests after all
	code changes. High ranked package ESPResSo does this.
	\item Reproducibility. Consider peer review processes and task based
	inspection to assess contributions. High ranked package ESPResSo does this.
	\item Unambiguity. Consider asking users for feedback on the documentation.
	The developer of pyLBM noted that such feedback would be appreciated.

@@

linters \citep{Zadka2018} were rarely observed in LBM projects.  Do not see much evidence of their presence in best practice guides.

@@

Our comparison may point out areas where some LBM software packages fall short
of current best practices.  This is not intended to be a criticism of any
existing packages, especially since in practice not every project needs to
achieve the highest possible quality.  However, rather than delve into the
nuances of which software can justify compromising which practice we will write
our comparison under the ideal assumption that every project can have sufficient
resources to match best practices.

@@

- should look at ReinerEtAl2022 on Domain of Ocean Modelling software to
contrast to the state of the practice of LBM software
